Kepler and the Behemoth: Three Mini-Neptunes in a 40 Million Year Old Association

### 2022-09-07 papers/paper_review/response_1.txt

REVIEWER COMMENT
----------
Line 225: Phrasing makes it sound like Cep-Her candidates observed by Kepler are distinct from those in RSG-5 and CH-2, but I assume they overlap?
RESPONSE
----------
> Yes, there is overlap.  But the set of Cep-Her stars that Kepler observed is a distinct set from the described sets of candidate stars in RSG-5 and CH-2.  The wording has been adjusted.

REVIEWER COMMENT
----------
Line 235: May be useful to readers to specify which part of Gaia Collaboration + 2018 the data filters are listed.
RESPONSE
----------
> We now include a reference to appendix B of Gaia Collaboration+2018.

REVIEWER COMMENT
----------
Line 246: "set the color range" had me looking for a color map, suggest saying "color axis" instead
RESPONSE
----------
> Done

REVIEWER COMMENT
----------
Line 251: This struck me as an odd use of "control sample" since delta Lyra seems like just another example equivalent to RSG-5 and CH-2
RESPONSE
----------
> We now call it a "reference sample".  It is indeed another example, equivalent to RSG-5 and CH-2.  The only difference is that it was studied in our earlier Kepler-1627 paper, where the explicit comparison against IC-2602 was made (Figure 3 of that work).

@@

REVIEWER COMMENT
----------
Line 359: Stars are referred to by spectral types, but then define ZAMS in terms of mass so it is not possible to compare without additional information about the spectral type of the sun on the ZAMS.
RESPONSE
----------
> We do not entirely understand what, if any, change is requested:  the purpose of these sentences is to give a broad-brush overview of the stellar properties.  The rough implicit understanding that the Sun would be "near" G2V at ZAMS (while in reality perhaps being a little less bright, and a little lower surface gravity) provides the necessary context that the stars being discussed spanning G8V to K6V are less massive than the Sun, and given ~40 Myr ages, therefore on the pre-main-sequence.

REVIEWER COMMENT
----------
*Table 1: Please specify which component of the binary KOI 7913 orbits
RESPONSE
----------
> A table note has been added.

REVIEWER COMMENT
----------
Line 364: From later comparisons with the spectroscopy, it seems that the MIST analysis also returns Teff.
RESPONSE
----------
> Yes -- please see the response to Line 449 below.

REVIEWER COMMENT
----------
Line 365: Clarify what is interpolating against the MIST isochrones.
RESPONSE
----------
> The interpolation is performed in the dimensions of reddening-corrected absolute $G$-band magnitude versus (BP-RP)0 color.  This clarification has been added.

### 2022-09-07 papers/paper/ms.tex
correct typos

In this work, we leverage recent analyses of the Gaia data, which have
greatly expanded our knowledge of stellar groups
\citep[{e.g.},][]{CantatGaudin2018a,KounkelCovey2019,Kerr2021}.
\replaced{To date these analyses have mostly clustered on stellar
positions and 2D velocities}{So far, these analyses have mostly
leveraged 3D stellar positions and 2D on-sky tangential velocities.}.
One important result has been the discovery of diffuse
streams and tidal tails comparable in stellar mass to the previously
known cores of nearby open clusters
\citep{meingast_psceri_2019,Meingast2021,gagne_number_2021}.  Even
though these streams are spread over tens to hundreds of parsecs,
their velocity dispersions can remain coherent at the $\sim$1\kms\
level.  Internal dynamics and projection effects can also drive them
to be much \replaced{larger}{more kinematically diffuse}: in the Hyades, stars in the tidal tails are
expected to span up to $\pm 40\mkms$ in velocity relative to the
cluster center \citep{jerabkova_800_2021}.  The stars in such diffuse
regions can be verified to be the same age as the core cluster members
through analyses of color--absolute magnitude diagrams
\citep{KounkelCovey2019}, stellar rotation periods
\citep{curtis_tess_2019,bouma_2021_ngc2516}, and chemical abundances
\citep{hawkins_2020,2020A&A...635L..13A}.  While there are implications for our
understanding of star formation and cluster evolution
\citep{dinnbier_tidal_2020}, a separate consequence is that we now
know the ages of many more stars, including previously known planet
hosts.

@@

The possibility that the $\delta$~Lyr cluster, RSG-5, and the
sub-populations identified by \citet{Kerr2021} share a common origin
has yet to be fully substantiated, but preliminary clustering results
from the 1\,kpc SPYGLASS analysis (R.~Kerr et al.\ in prep) suggest
the presence of contiguous stellar populations connecting each of
these groups in \replaced{space-velocity}{both space and velocity} coordinates.  In other words, the stars
appear to be comoving, though with a continuous gradient in velocity
as a function of position\replaced{ (Figure~\ref{fig:XYZvtang}, lower
panels).}{. The lower panels of Figure~\ref{fig:XYZvtang} show this in
detail, where $v_b$ is the distance-corrected proper motion in the
direction of increasing galactic latitude, and $v_{l^*}=v_l \cos b$ is
the distance-corrected proper motion in the direction of increasing
galactic longitude after accounting for the local tangent plane
correction.  Some, but not all, of the gradient in the $v_{l^*}$ {\it vs.}~$l$
plane can be understood through a projection effect stemming from the
Sun's motion with respect to the local standard of rest (see also
Figure 11 by \citet{Zari2018}).  }
In this work, our primary interest in \replaced{the region}{this
region of sky} stems
from the fact that a portion of it was observed by Kepler
(Figure~\ref{fig:XYZvtang}, top panel).  To further explore this
sub-population, we select candidate Cep-Her members through four
steps, the first three being identical to those described in Section~3
of \citet{Kerr2021}.  We briefly summarize them here.

@@

The CAMDs show that for RSG-5, all but one of the candidate
members are on a tight pre-main-sequence locus.  \added{Quantitatively,
88/89 stars with $\bpmrpo \geq 1.5$ are consistent with being on the
pre-main-sequence.} This implies a false
positive rate of a few percent, at most.  In comparison, our \replaced{control}{comparison}
sample (the $\delta$~Lyr candidates) has a false positive rate of
$\approx$12\%, based on the number of stars that photometrically
overlap with the field population\deleted{, while being outliers from the bulk
cluster population}.  For CH-2, our membership selection gives 27
objects in the color range displayed, and 23 of them appear to be
consistent with being on the pre-main-sequence.  This
\replaced{implies}{would imply} a false
positive rate in CH-2 of $\approx$15\%.

Figure~\ref{fig:age} also shows that most RSG-5 and CH-2 members
overlap with the $\delta$~Lyr cluster\added{ on the CAMD}, and that the groups are
therefore roughly the same age.  To quantify this, we use the method
introduced by \citet[][their Section~6.3]{gagne_mutau_2020}.  The idea
is to fit the pre-main-sequence loci of a set of reference clusters,
and to then model the locus of the target cluster as a linear
combination of these reference cluster loci.  For our reference
clusters, we used UCL, IC\,2602, and the Pleiades, with the
memberships reported by \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We adopted ages of 16\,Myr for
UCL \citep{pecaut_star_2016}, 38\,Myr for IC\,2602
\citep{david_ages_2015,randich_gaiaeso_2018} and 112\,Myr for the
Pleiades \citep{dahm_2015}.  These assumptions and the subsequent
processing steps taken to exclude field stars and binaries were
identical to those described in \citet{bouma_kep1627_2022}.  The mean
and uncertainty of the resulting age posterior are $46^{+9}_{-7}$\,Myr
for RSG-5, and $36^{+10}_{-8}$\,Myr for CH-2.  For comparison, this
procedure yields an age for the $\delta$~Lyr cluster of
$38^{+6}_{-5}$\,Myr.  The older isochronal age of RSG-5 is consistent
with its location relative to the $\delta$~Lyr cluster in the upper
left panel of Figure~\ref{fig:age}.
Generally speaking, this method is expected to be accurate provided
that the metallicities of IC\,2602 and the Cep-Her groups (RSG-5,
CH-2, and the $\delta$~Lyr cluster) are roughly identical.  The
spectroscopic metallicities that we find in Section~\ref{sec:stars}
suggest that this is indeed the case.
\added{While in reality stellar populations do not evolve linearly in
the dimensions of absolute magnitude versus color, in our case the
Cep-Her loci are nearly indistinguishable from IC\,2602 (e.g.,
Figure~3 of \citet{bouma_kep1627_2022}).  Systematic errors incurred
in the age from the non-linear evolution are therefore likely much
smaller than the $\approx$10\,Myr systematic uncertainty in the
absolute reference age for IC\,2602 itself
\citep{david_ages_2015,randich_gaiaeso_2018}.}

@@

The lower panels of Figure~\ref{fig:age} show the results.  In RSG-5,
\replaced{41/47}{39/42} stars have rotation periods \replaced{faster
than}{at least as fast as} the Pleiades (\replaced{87}{93}\%).  This
numerator omits the two stars with periods $>$$12$\,days visible in
the lower-left panel of Figure~\ref{fig:age}.  The age interpretation
for these latter stars, particularly the $\approx$M2.5 dwarf, is not
obvious.  \citet{rebull_usco_2018} for instance have found numerous
M-dwarfs with 10-12 day rotation periods at ages of USco
($\sim$$8$\,Myr), and some \deleted{may} still exist at ages of
LCC ($\sim$$16$\,Myr; \replaced{L.~Rebull
submitted}{\citealt{2022AJ....164...80R}}).  Regardless, since
\replaced{nearly no field star outliers seem}{only one field star
outlier seems} to be present on the RSG-5 CAMD,
the fact
that we do not detect rotation periods for $\approx$\replaced{13}{7}\%
of stars should perhaps be taken as an indication for the fraction of
stars for which rotation periods might not be detectable, due to
{e.g.}, pole-on stars having lower amplitude starspot modulation.
\added{Field star contamination is another possible contributor.}

@@

The adopted stellar parameters are listed in
Table~\ref{tab:sysparams}.  The stellar surface gravity, radius, mass,
and density are found by interpolating against the MIST isochrones
\added{in absolute reddening-corrected $G$-band magnitude as a function of $\bpmrpo$\ color}
\citep{choi_mesa_2016}.  The statistical uncertainties from this
technique mostly originate from the parallax uncertainties; the
systematic uncertainties are taken to be the absolute difference
between the PARSEC \citep{bressan_parsec_2012} and MIST isochrones.
Reported uncertainties are a quadrature sum of the statistical and
systematic components.

@@

\paragraph{Spectra}
For Kepler-1643, we acquired two iodine-free spectra from Keck/HIRES
on the nights of 2020 Aug 16 and 2021 Oct 25.  The acquisition and
analysis followed the usual techniques of the California Planet Survey
\citep{howard_cps_2010}.  We derived the stellar parameters ($T_{\rm
eff}, \log g, R_\star$) using \texttt{SpecMatch-Emp}
\citep{yee_SM_2017}, which yielded values in $<$$1$-$\sigma$ agreement
with those from the cluster-isochrone method.  This approach also
yielded $[{\rm Fe/H}]=0.13 \pm 0.09$.  Using the broadened synthetic
templates\added{\footnote{The broadening is calculated using the joint
rotational and macroturbulent broadening kernel from \citet{hirano_2011},
assuming that the macroturbulent velocity scales with effective temperature similar
to the prescription from \citet{2014MNRAS.444.3592D}.  The latter assumption could be a 
source of systematic uncertainty in our equatorial velocity measurements, since
the macroturbulent velocity could be systematically higher (or lower) on
the pre-main-sequence than it is for more slowly rotating field stars.}}
 from \texttt{SpecMatch-Synth} \citep{petigura_cksi_2017}, we
found $v\sin i = 9.3 \pm 1.0\,\mkms$.  The systemic radial velocity at
the two epochs was $-9.1 \pm 1.9\,\mkms$ and $-7.8\pm 1.2\,\mkms$
respectively\replaced{ \citep{chubak_2012}}{, and was calculated
following the methods of \citet{chubak_2012}}.  To infer the equivalent width of
the \ion{Li}{1} 6708\,\AA\ doublet, we followed the procedure
described by \citet{bouma_2021_ngc2516}. \added{In brief, this
involved a Monte Carlo procedure in which the continuum normalization
was allowed to vary through a bootstrap approach based on the local
scatter, and the line width itself was calculated by integrating a
single Gaussian over a local window.}  For Kepler-1643, this yielded a
strong detection: ${\rm EW}_{\rm Li} = 130^{+6}_{-5}$\,m\AA, with
values consistent at $<$$1$-$\sigma$ between the two epochs.   The
quoted value does not correct for the \ion{Fe}{1} blend at
6707.44\,\AA.  Given the purported age and effective temperature of
the star, the lithium equivalent width is somewhat low.  We discuss
this in greater depth in Section~\ref{subsec:specyouth}.

@@

\paragraph{Binarity}
KOI-7913 is a binary.  The north-west primary is
$\approx$0.5 magnitudes brighter than the south-east secondary in
optical passbands.  The two stars are separated in Gaia EDR3 by
$3\farcs5$ on-sky, and have parallaxes consistent within $1$-$\sigma$
(with an average $\varpi=3.66 \pm 0.01$\,mas).  The apparent on-sky
separation is $959 \pm 2$ au.  The Gaia EDR3 proper motions are also
very similar.  Since two stars were resolved in the Kepler Input
Catalog and are roughly one Kepler pixel apart, an accurate crowding
metric has already been applied in the NASA Ames data products to
correct the mean flux level \citep{2017ksci.rept....6M}.  This is
important for deriving accurate transit depths.

@@

Kepler-1643, in RSG-5, is conspicuously below the 40-50$\,$Myr
sequence in the left-panel of Figure~\ref{fig:lithium}, though
above the field stars (${\rm EW}_{\rm Li} = 130^{+6}_{-5}$\,m\AA).
added{
Quantitatively, there are 14 reference stars within $\pm$150\,K of Kepler-1643.
The mean and standard deviation of their lithium EWs is $255 \pm 31$\,m\AA,
which implies that Kepler-1643 is $4.0$-$\sigma$ discrepant from expectations.
}
The right panel shows the comparison against the Pleiades, where
Kepler-1643 is more consistent with the observed dispersion in
lithium.

@@

Our preferred explanation for Kepler-1643's meager lithium 
content is that the reference sample\added{s} of IC\,2602 and Tuc-Hor
stars may not fully explore all possible stellar rotation
periods and lithium equivalent widths at this age.
\added{This would be somewhat surprising since over a dozen stars have
already been analyzed in the relevant effective temperature range.
However, considering}
the top panels of Figure~\ref{fig:lithium}, it is \added{also} remarkable that in
50 million years, stars between $4500$\,K and $5200$\,K go from
having a tight lithium sequence to one with a dispersion
$\approx10\times$ greater.  The existence of the Li dispersion in
Pleiades-age K-dwarfs has been known for decades; it has also been
known that the stars with the largest lithium abundances are also the
most rapidly rotating
\citep{butler_pleiades_1987,soderblom_evolution_1993}.  More recent
analyses of this correlation have been reviewed by
\citet{bouvier_lithium-rotation_2020}.  The conclusion of that work
was that the origin of the rotation-lithium correlation likely lies
within pre-main-sequence stellar physics.  If so, one would expect the
IC\,2602 and Tuc-Hor K-dwarfs to show a larger intrinsic lithium
dispersion.  A recent analysis of the $\approx$40\,Myr
NGC~2547 by \citet{binks_2022} suggests that this may
be the case, though that study only had $\approx$10 stars in the relevant
effective temperature range.
\added{An alternative explanation could be that the overall metallicity of Cep-Her
is different from Tuc-Hor and IC\,2602, but this seems unlikely given the near-solar
metallicities we have measured for the Kepler Objects of Interest.}
\replaced{This suggests that RSG-5 and Cep-Her could be worthy objects for a
closer analysis of the lithium-rotation correlation near the zero-age
main sequence.}{Broadly, these considerations suggest that Cep-Her is
a worthy object for further spectroscopic analyses of lithium near the
zero-age main sequence.}

@@

Balmer line emission, particularly in H$\alpha$, is expected for
low-mass stars of this age.  \citet{kraus_stellar_2014} for instance, in their
survey of Tuc-Hor ($\approx$40\,Myr), observed that all
cluster members with spectral types $>$${\rm K4.5V}$ had H$\alpha$ in
emission.  This is consistent with our observations: KOI-7913 shows
H$\alpha$ in emission for both components, and in absorption
for all of our other Kepler objects (Figure~\ref{fig:koiyouthindicators}, lower panel).  The double-peaked nature of the
emission, though not always present, is also common for
active stars.  Proxima Centauri, for instance, has double-peaked
H$\alpha$ emission \citep{collins_calculations_2017}.  Given
that we have ruled out spectroscopic binarity, the most
likely
explanation is self-absorption: photons near the center of the line
see a greater optical depth from higher layers of the chromosphere,
while photons on the wings are too far from the
rest-wavelength to excite electrons and be re-absorbed in the upper
layers.  The exact details of when a star's atmosphere reaches the
conditions for such self-absorption require non-local thermal
equilibrium models of the chromosphere
\citep{short_chromospheric_1998,2005A&A...439.1137F}.

@@

It bears mentioning that KOI-7368 shows a centroid shift in the
\texttt{q1\_q17\_dr25\_koi} validation reports, similar to
Kepler-1643.  For KOI-7368, the reported offset is smaller, and less
\added{formally }significant ($0\farcs2$; 3.0-$\sigma$).  Again, the
data validation reports show that the shift is caused by a few
outlying quarters (4, 5, 8, and 12).  Since the remaining data show
consistent scatter in their centroid locations, these outlying
quarters are likely also caused by the stellar variability\added{,
since their directions across different quarters are inconsistent}.
Our NIRC2 imaging independently shows that there are no \added{known
}neighboring sources that could cause an offset of the observed
amplitude\added{, as is also the case for Kepler-1643}.

@@

The theoretical expectation is that mini-Neptunes with sizes of 2 to
3\,$R_\oplus$ should be common at ages of $10^7$ to $10^8$ years.
This expectation is tied to inferences about the initial distributions
of planetary core mass, core composition, and atmospheric mass
fraction \citep{owen_evaporation_2017}.  The Kelvin-Helmholtz cooling
timescale, which is tied to the entropy of the planetary interior
shortly after disk dispersal, also plays a significant role
\citep{owen_constraining_2020}.  As an example,
\citet{rogers_unveiling_2021} predicted that given a core mass
distribution peaked at $\approx$$4$\,$M_\oplus$, an ice-poor rock/iron
core composition, and a typical H/He mass fraction of $\approx$4\%,
there should be a local maximum in planet occurrence rates at 2 to 3\,$R_\oplus$,
at times between 10 and 100\,Myr.  The models advanced by
\citet{gupta_signatures_2020} and \citet{lee_primordial_2021} agree;
their differences lie in the mechanism for producing the radius
valley, and in whether a population of rocky planets is predicted to exist
at the time of disk dispersal.

@@

% \clearpage
\bibliographystyle{yahapj}                            
\bibliography{bibliography}

>>>>

In this work, we leverage recent analyses of the Gaia data, which have
greatly expanded our knowledge of stellar groups
\citep[{e.g.},][]{CantatGaudin2018a,KounkelCovey2019,Kerr2021}.
\replaced{To date these analyses have mostly clustered on stellar
positions and 2D velocities}{So far, these analyses have mostly
leveraged 3D stellar positions and 2D on-sky tangential velocities}.
One important result has been the discovery of diffuse
streams and tidal tails comparable in stellar mass to the previously
known cores of nearby open clusters
\citep{meingast_psceri_2019,Meingast2021,gagne_number_2021}.  Even
though these streams are spread over tens to hundreds of parsecs,
their velocity dispersions can remain coherent at the $\sim$1\kms\
level.  Internal dynamics and projection effects can also drive them
to be much \replaced{larger}{more kinematically diffuse}: in the Hyades, stars in the tidal tails are
expected to span up to $\pm 40\mkms$ in velocity relative to the
cluster center \citep{jerabkova_800_2021}.  The stars in such diffuse
regions can be verified to be the same age as the core cluster members
through analyses of color--absolute magnitude diagrams
\citep{KounkelCovey2019}, stellar rotation periods
\citep{curtis_tess_2019,bouma_2021_ngc2516}, and chemical abundances
\citep{hawkins_2020,2020A&A...635L..13A}.  While there are implications for our
understanding of star formation and cluster evolution
\citep{dinnbier_tidal_2020}, a separate consequence is that we now
know the ages of many more stars, including previously known planet
hosts.

@@

The possibility that the $\delta$~Lyr cluster, RSG-5, and the
sub-populations identified by \citet{Kerr2021} share a common origin
has yet to be fully substantiated, but preliminary clustering results
from the 1\,kpc SPYGLASS analysis (R.~Kerr et al.\ in prep) suggest
the presence of contiguous stellar populations connecting each of
these groups in \replaced{space-velocity}{both space and velocity} coordinates.  In other words, the stars
appear to be comoving, though with a continuous gradient in velocity
as a function of position\replaced{ (Figure~\ref{fig:XYZvtang}, lower
panels).}{. The lower panels of Figure~\ref{fig:XYZvtang} show this in
detail, where $v_b$ is the distance-corrected proper motion in the
direction of increasing galactic latitude, and $v_{l^*}=v_l \cos b$ is
the distance-corrected proper motion in the direction of increasing
galactic longitude after accounting for the local tangent plane
correction.  Some, but not all, of the gradient in the $v_{l^*}$ vs.~$l$
plane can be understood through a projection effect stemming from the
Sun's motion with respect to the local standard of rest (see also
Figure 11 by \citealt{Zari2018}).  }
In this work, our primary interest in \replaced{the region}{this
region of sky} stems
from the fact that a portion of it was observed by Kepler
(Figure~\ref{fig:XYZvtang}, top panel).  To further explore this
sub-population, we select candidate Cep-Her members through four
steps, the first three being identical to those described in Section~3
of \citet{Kerr2021}.  We briefly summarize them here.

@@

The CAMDs show that for RSG-5, all but one of the candidate
members are on a tight pre-main-sequence locus.  \added{Quantitatively,
88/89 stars with $\bpmrpo \geq 1.5$ are consistent with being on the
pre-main-sequence.} This implies a false
positive rate of a few percent, at most.  In comparison, our
\replaced{control}{reference}
sample (the $\delta$~Lyr candidates) has a false positive rate of
$\approx$12\%, based on the number of stars that photometrically
overlap with the field population\deleted{, while being outliers from the bulk
cluster population}.  For CH-2, our membership selection gives 27
objects in the color range displayed, and 23 of them appear to be
consistent with being on the pre-main-sequence.  This
\replaced{implies}{would imply} a false
positive rate in CH-2 of $\approx$15\%.

Figure~\ref{fig:age} also shows that most RSG-5 and CH-2 members
overlap with the $\delta$~Lyr cluster\added{ on the CAMD}, and that the groups are
therefore roughly the same age.  To quantify this, we use the method
introduced by \citet[][their Section~6.3]{gagne_mutau_2020}.  The idea
is to fit the pre-main-sequence loci of a set of reference clusters,
and to then model the locus of the target cluster as a linear
combination of these reference cluster loci.  For our reference
clusters, we used UCL, IC\,2602, and the Pleiades, with the
memberships reported by \citet{Damiani2019} and
\cite{CantatGaudin2018a} respectively.  We adopted ages of 16\,Myr for
UCL \citep{pecaut_star_2016}, 38\,Myr for IC\,2602
\citep{david_ages_2015,randich_gaiaeso_2018} and 112\,Myr for the
Pleiades \citep{dahm_2015}.  These assumptions and the subsequent
processing steps taken to exclude field stars and binaries were
identical to those described in \citet{bouma_kep1627_2022}.  The mean
and uncertainty of the resulting age posterior are $46^{+9}_{-7}$\,Myr
for RSG-5, and $36^{+10}_{-8}$\,Myr for CH-2.  For comparison, this
procedure yields an age for the $\delta$~Lyr cluster of
$38^{+6}_{-5}$\,Myr.  The older isochronal age of RSG-5 is consistent
with its location relative to the $\delta$~Lyr cluster in the upper
left panel of Figure~\ref{fig:age}.
Generally speaking, this method is expected to be accurate provided
that the metallicities of IC\,2602 and the Cep-Her groups (RSG-5,
CH-2, and the $\delta$~Lyr cluster) are roughly identical.  The
spectroscopic metallicities that we find in Section~\ref{sec:stars}
suggest that this is indeed the case.
\added{While in reality stellar populations do not evolve linearly in
the dimensions of absolute magnitude versus color, in our case the
Cep-Her loci are nearly indistinguishable from IC\,2602 (e.g.,
Figure~3 of \citealt{bouma_kep1627_2022}).  Systematic errors incurred
in the age from the non-linear evolution are therefore likely much
smaller than the $\approx$10\,Myr systematic uncertainty in the
absolute reference age for IC\,2602 itself
\citep{david_ages_2015,randich_gaiaeso_2018}.}

@@

The lower panels of Figure~\ref{fig:age} show the results.  In RSG-5,
\replaced{41/47}{39/42} stars have rotation periods \replaced{faster
than}{at least as fast as} the Pleiades (\replaced{87}{93}\%).  This
numerator omits the two stars with periods $>$$12$\,days visible in
the lower-left panel of Figure~\ref{fig:age}.  The age interpretation
for these latter stars, particularly the $\approx$M2.5 dwarf, is not
obvious.  \citet{rebull_usco_2018} for instance have found numerous
M-dwarfs with 10-12 day rotation periods at ages of USco
($\sim$$8$\,Myr), and some \deleted{may} still exist at the age of
LCC ($\sim$$16$\,Myr; \replaced{L.~Rebull
submitted}{\citealt{2022AJ....164...80R}}).  Regardless, since
\replaced{nearly no field star outliers seem}{only one field star
outlier seems} to be present on the RSG-5 CAMD,
the fact
that we do not detect rotation periods for $\approx$\replaced{13}{7}\%
of stars should perhaps be taken as an indication for the fraction of
stars for which rotation periods might not be detectable, due to
{e.g.}, pole-on stars having lower amplitude starspot modulation.
\added{Field star contamination is another possible contributor.}

@@

The adopted stellar parameters are listed in
Table~\ref{tab:sysparams}.  The stellar surface gravity, radius, mass,
and density are found by interpolating against the MIST isochrones
\added{in reddening-corrected absolute $G$-band magnitude as a function of $\bpmrpo$\ color}
\citep{choi_mesa_2016}.  The statistical uncertainties from this
technique mostly originate from the parallax uncertainties; the
systematic uncertainties are taken to be the absolute difference
between the PARSEC \citep{bressan_parsec_2012} and MIST isochrones.
Reported uncertainties are a quadrature sum of the statistical and
systematic components.

@@

\paragraph{Spectra}
For Kepler-1643, we acquired two iodine-free spectra from Keck/HIRES
on the nights of 2020 Aug 16 and 2021 Oct 25.  The acquisition and
analysis followed the usual techniques of the California Planet Survey
\citep{howard_cps_2010}.  We derived the stellar parameters ($T_{\rm
eff}, \log g, R_\star$) using \texttt{SpecMatch-Emp}
\citep{yee_SM_2017}, which yielded values in $<$$1$-$\sigma$ agreement
with those from the cluster-isochrone method.  This approach also
yielded $[{\rm Fe/H}]=0.13 \pm 0.09$.  Using the broadened synthetic
templates\added{\footnote{The broadening is calculated using the joint
rotational and macroturbulent broadening kernel from \citet{hirano_2011},
assuming that the macroturbulent velocity scales with effective temperature similar
to the prescription from \citet{2014MNRAS.444.3592D}.  The latter assumption could be a 
source of systematic uncertainty in our equatorial velocity measurements, since
the macroturbulent velocity could be systematically higher (or lower) on
the pre-main-sequence than it is for more slowly rotating field stars.}}
 from \texttt{SpecMatch-Synth} \citep{petigura_cksi_2017}, we
found $v\sin i = 9.3 \pm 1.0\,\mkms$.  The systemic radial velocity at
the two epochs was $-9.1 \pm 1.9\,\mkms$ and $-7.8\pm 1.2\,\mkms$
respectively\replaced{ \citep{chubak_2012}}{, and was calculated
following the methods of \citet{chubak_2012}}.  To infer the equivalent width of
the \ion{Li}{1} 6708\,\AA\ doublet, we followed the procedure
described by \citet{bouma_2021_ngc2516}. \added{In brief, this
involved calculating the line width by numerically integrating a
single best-fit Gaussian over a local window, and estimating the
uncertainties through a Monte Carlo procedure in which the continuum
normalization was allowed to vary through a bootstrap approach based
on the local scatter in the spectra.}  For Kepler-1643, this yielded a
strong detection: ${\rm EW}_{\rm Li} = 130^{+6}_{-5}$\,m\AA, with
values consistent at $<$$1$-$\sigma$ between the two epochs.   The
quoted value does not correct for the \ion{Fe}{1} blend at
6707.44\,\AA.  Given the purported age and effective temperature of
the star, the lithium equivalent width is somewhat low.  We discuss
this in greater depth in Section~\ref{subsec:specyouth}.

@@

\paragraph{Binarity}
KOI-7913 is a binary.  The north-west primary is
$\approx$0.5 magnitudes brighter than the south-east secondary in
optical passbands.  The two stars are separated in Gaia EDR3 by
$3\farcs5$ on-sky, and have parallaxes consistent within $1$-$\sigma$
(with an average $\varpi=3.66 \pm 0.01$\,mas).  The apparent on-sky
separation is $959 \pm 2$ au.  The Gaia EDR3 proper motions are also
very similar.  Since the two stars were resolved in the Kepler Input
Catalog and are roughly one Kepler pixel apart, an accurate crowding
metric has already been applied in the NASA Ames data products to
correct the mean flux level \citep{2017ksci.rept....6M}.  This is
important for deriving accurate transit depths.

@@

Kepler-1643, in RSG-5, is conspicuously below the 40-50$\,$Myr
sequence in the \replaced{left-panel}{top panel} of Figure~\ref{fig:lithium}, though
above the field stars (${\rm EW}_{\rm Li} = 130^{+6}_{-5}$\,m\AA).
\added{
Quantitatively, there are 14 reference stars within $\pm$150\,K of Kepler-1643.
The mean and standard deviation of their lithium EWs is $255 \pm 31$\,m\AA,
which implies that Kepler-1643 is $4.0$-$\sigma$ discrepant from expectations.
}
The \replaced{right}{middle} panel shows \replaced{the}{a} comparison against the Pleiades, where
Kepler-1643 is more consistent with the observed dispersion in
lithium.

@@

Our preferred explanation for Kepler-1643's meager lithium 
content is that the reference sample\added{s} of IC\,2602 and Tuc-Hor
stars may not fully explore all possible \deleted{stellar rotation
periods and }lithium equivalent widths at this age.
\added{This would be somewhat surprising since over a dozen stars have
already been analyzed in the relevant effective temperature range.
However, considering}
the top panels of Figure~\ref{fig:lithium}, it is \added{also} remarkable that in
50 million years, stars between $4500$\,K and $5200$\,K go from
having a tight lithium sequence to one with a dispersion
$\approx$$10\times$ greater.  The existence of the Li dispersion in
Pleiades-age K-dwarfs has been known for decades; it has also been
known that the stars with the largest lithium abundances are also the
most rapidly rotating
\citep{butler_pleiades_1987,soderblom_evolution_1993}.  More recent
analyses of this correlation have been reviewed by
\citet{bouvier_lithium-rotation_2020}.  The conclusion of that work
was that the origin of the rotation-lithium correlation likely lies
within pre-main-sequence stellar physics.  If so, one would expect the
IC\,2602 and Tuc-Hor K-dwarfs to show a larger intrinsic lithium
dispersion.  A recent analysis of the $\approx$40\,Myr
NGC~2547 by \citet{binks_2022} suggests that this may
be the case, though that study only had $\approx$10 stars in the relevant
effective temperature range.
\added{An alternative explanation could be that the overall metallicity of Cep-Her
is different from Tuc-Hor and IC\,2602, but this seems unlikely given the near-solar
metallicities we have measured for the Kepler Objects of Interest.}
\replaced{This suggests that RSG-5 and Cep-Her could be worthy objects for a
closer analysis of the lithium-rotation correlation near the zero-age
main sequence.}{Broadly, these considerations suggest that Cep-Her is
a worthy object for further spectroscopic analyses of lithium near the
zero-age main sequence.}

@@

Balmer line emission, particularly in H$\alpha$, is expected for
low-mass stars of this age.  \citet{kraus_stellar_2014} for instance, in their
survey of Tuc-Hor ($\approx$40\,Myr), observed that all
cluster members with spectral types $>$${\rm K4.5V}$ had H$\alpha$ in
emission.  This is consistent with our observations: KOI-7913 shows
H$\alpha$ in emission for both components, and in absorption
for all of our other Kepler objects (Figure~\ref{fig:koiyouthindicators}, lower panel).  The double-peaked nature of the
emission, though not always present, is also common for
active stars.  Proxima Centauri, for instance, has double-peaked
H$\alpha$ emission \citep{collins_calculations_2017}.  Given
that we have ruled out spectroscopic binarity, the most
likely
explanation is self-absorption: photons near the center of the line
see a greater optical depth from higher layers of the chromosphere,
while photons on the wings are too far from the
rest wavelength to excite electrons and be re-absorbed in the upper
layers.  The exact details of when a star's atmosphere reaches the
conditions for such self-absorption require non-local thermal
equilibrium models of the chromosphere
\citep{short_chromospheric_1998,2005A&A...439.1137F}.

@@

It bears mentioning that KOI-7368 shows a centroid shift in the
\texttt{q1\_q17\_dr25\_koi} validation reports, similar to
Kepler-1643.  For KOI-7368, the reported offset is smaller, and less
\added{formally }significant ($0\farcs2$; 3.0-$\sigma$).  Again, the
data validation reports show that the shift is caused by a few
outlying quarters (4, 5, 8, and 12).  Since the remaining
\replaced{data}{quarters} show
consistent scatter in their centroid locations, these outlying
quarters are likely also caused by the stellar variability\added{,
because their directions are inconsistent across different quarters}.
Our NIRC2 imaging independently shows that there are no \added{known
}neighboring sources that could cause an offset of the observed
amplitude\added{, as is also the case for Kepler-1643}.

@@

The theoretical expectation is that mini-Neptunes with sizes of 2 to
3\,$R_\oplus$ should be common at ages of $10^7$ to $10^8$ years.
This expectation is tied to inferences about the initial distributions
of planetary core mass, core composition, and atmospheric mass
fraction \citep{owen_evaporation_2017}.  The Kelvin-Helmholtz cooling
timescale, which is tied to the entropy of the planetary interior
shortly after disk dispersal, also plays a significant role
\citep{owen_constraining_2020}.  As an example,
\citet{rogers_unveiling_2021} predicted that given a core mass
distribution peaked at $\approx$$4$\,$M_\oplus$, an ice-poor rock/iron
core composition, and a typical H/He mass fraction of $\approx$4\%,
there should be a \added{single} local maximum in planet occurrence rates at 2 to 3\,$R_\oplus$,
at times between 10 and 100\,Myr. \added{In other words,
\citet{rogers_unveiling_2021} predict the existence of a ``radius
mountain'' at these early times, rather than a ``radius valley''.}  The models advanced by
\citet{gupta_signatures_2020} and \citet{lee_primordial_2021}
agree\added{ that this local maximum should exist};
their differences lie in the mechanism for producing the radius
valley, and in whether a population of rocky planets is predicted to exist
at the time of disk dispersal.

@@

\clearpage
\bibliographystyle{yahapj}                            
\bibliography{bibliography}
